Supplementary material for ``Screening Sinkhorn Algorithm for regularized Optimal Transport''

### 2019-05-17 tex/v3/section_4_marginal_viols.tex
new

Using the facts that $\varepsilon \leq (mnK_{\min}^2)^{-1/4}$ and $\kappa \leq \sqrt{m/(nK_{\min})}$, we can get a closed forms of~\eqref{maginal_mu} and~\eqref{maginal_nu} depending on $n,m,K_{\min}$, the budgets $n_b,m_b,$ and $c_{\mu\nu} = \underline{\mu}\wedge \underline{\nu}$ with $\underline{\mu} = \min_{i\in I_{\varepsilon,\kappa}}\mu_i, \underline{\nu} = \min_{j\in J_{\varepsilon,\kappa}}\nu_j$ as follows:
{\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_\kappa + (n- n_b) \bigg[\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}{K_{\min}}}
 + \log\bigg(\frac{(n-n_b+1)\sqrt{m}}{m_b \sqrt{n}K_{\min}^{3/2}\underline{\nu}} 
\bigg)\bigg]\Bigg)

>>>>

%Using the facts that $\varepsilon \leq (mnK_{\min}^2)^{-1/4}$ and $\kappa \leq \sqrt{m/(nK_{\min})}$, 
% We can get a closed forms of~\eqref{maginal_mu} and~\eqref{maginal_nu} depending on $n,m,K_{\min}$, the budgets $n_b,m_b,$ and $c_{\mu\nu} = \underline{\mu}\wedge \underline{\nu}$ with $\underline{\mu} = \min_{i\in I_{\varepsilon,\kappa}}\mu_i, \underline{\nu} = \min_{j\in J_{\varepsilon,\kappa}}\nu_j$ as follows:
% {\norm{{\mu} -{\mu}^{\text{sc}}}^2_1} = \bigO\Bigg(n_bc_\kappa + (n- n_b) \bigg[\frac{m_b}{\sqrt{nmc_{\mu\nu}}K_{\min}^{3/2}} &+ \frac{m-m_b}{\sqrt{nm}{K_{\min}}}
% \bigg)\bigg]\Bigg)
